Supporting Information: Improving cropland maps through tight integration of human and machine intelligence

### 2021-02-22 inst/manuscript/figures.Rmd
Edits for average field size text (SI, ms), and regression kriging adjustments (not to be retained), as well as new tile-wise presentation (figures).

### Figure 7: Categorical map accuracy
Place map accuracy tables and zone report into single figure, for AOI zones.

@@

# gp <- t1 + m
ggsave(t1, filename = pth("figures/figure7.png"), width = 7, height = 7.9, 
       units = "in", dpi = 300)
```

### Figure 8: Cropland maps
```{r, eval=FALSE}
# segment files
segment_files <- dir(here("external/data/results/segments/merged"),
                     pattern = "boundarymerge", full.names = TRUE)
iid <- as.numeric(gsub("[[:alpha:]]|_|\\.", "", basename(segment_files)))
segment_files <- tibble(file = segment_files, order = iid) %>% arrange(iid)
segment_files <- segment_files %>% filter(!grepl("aoi3_*.*merge.geojson", file))

@@

ggsave(filename = pth("figures/figure8.png"), 
       plot = inset_map, bg = "transparent", width = diff(maprange[1:2]), 
       height = diff(maprange[3:4]), units = "in", dpi = 300)

@@

@@

m2 <- ggplot(aez %>% filter(ID != 8)) + geom_sf(lwd = 0.1) +
  geom_sf(data = aez_zones, lwd = 0.5, fill = "transparent") + 
  geom_sf_text(data = st_centroid(aez_zones), aes(label = zone), size = 4) + 
  theme_void() + theme(plot.margin = unit(c(0, 0, 0, 0), "cm"))

ggsave(m + m2 + plot_annotation(tag_levels = 'A'), 
       filename = pth("figures/si_aoi_zones.png"), width = 3.5 * 2, 
       height = 4.5, units = "in", dpi = 300)
```

### Figure S10: AEZ accuracies

@@

### Figure S11: Segmentation statistics (grid scale)

[Check whether the means need to be weighted or not]
[Check whether need to redo median]
```{r segstats, eval=FALSE}
# data("top_label_data")
# data("field_validation_stats")
data("segment_quality_stats")
# data
datnms <- c("top_label_data", "field_validation_stats")#,
            # "tile_aoi_validation_stats")
for(i in datnms) {
  load(system.file(glue::glue("extdata/{i}.rda"), package = "activemapper"))
}

@@

>>>>

### Table 2: Categorical map accuracy
Place map accuracy tables and zone report into single figure, for AOI zones.

@@

# gp <- t1 + m
ggsave(t1, filename = pth("figures/table2.png"), width = 7, height = 7.9, 
       units = "in", dpi = 300)
```

### Figure 7: Cropland maps
```{r, eval=FALSE}
# segment files
segment_files <- dir(here("external/data/results/segments/merged"),
                     pattern = "boundarymerge", full.names = TRUE)
iid <- as.numeric(gsub("[[:alpha:]]|_|\\.", "", basename(segment_files)))
segment_files <- tibble(file = segment_files, order = iid) %>% arrange(iid)
segment_files <- segment_files %>% filter(!grepl("aoi3_*.*merge.geojson", file))

@@

ggsave(filename = pth("figures/figure7.png"), 
       plot = inset_map, bg = "transparent", width = diff(maprange[1:2]), 
       height = diff(maprange[3:4]), units = "in", dpi = 300)

@@

### Table 3
```{r, eval = FALSE}
fsizes_n_05 <- st_read(
  system.file("extdata/field_size_n_05.geojson", package = "activemapper")
) %>% mutate(
  muarea = ifelse(is.na(muarea), 0, muarea),
  nflds = ifelse(is.na(nflds), 0, nflds),
  aoi = as.character(aoi)
)

# calculate bias factors for adjustment
data("segment_quality_stats")
segment_quality_stats %>% filter(measure == "n")
biases <- segment_quality_stats %>%
  filter(Stat == "Mean" & scale == "grid") %>% 
  pivot_wider(names_from = type, values_from = value) %>% 
  mutate(bias = Validation - Segmentation, 
         biasfactor = Validation / Segmentation)
biases <- as_tibble(tiles) %>% group_by(aoi1) %>% 
  count() %>% ungroup() %>% 
  rename(aoi = aoi1, ntiles = n) %>% 
  mutate(aoi = as.character(aoi), ncells = ntiles * 100) %>% 
  left_join(biases, .) %>% 
  select(-scale, -Stat)
# biases %>% filter(measure == "n")
# tiles %>% slice(1) %>% raster::extract(mgridr, .)
# st_area(aois) / 10000 / 100

# apply bias adjustments
# field area first
fsizes_n_05_adj <- biases %>% filter(measure == "area" & aoi != "All") %>% 
  select(aoi, biasfactor) %>% 
  rename(fbias = biasfactor) %>% 
  left_join(fsizes_n_05, .) %>% 
  mutate(muarea_adj = muarea * fbias)

# then field count
fsizes_n_05_adj <- biases %>% filter(measure == "n" & aoi != "All") %>% 
  select(aoi, biasfactor, ntiles, ncells) %>% 
  rename(nbias = biasfactor) %>% 
  left_join(fsizes_n_05_adj, .) %>% 
  mutate(nflds_adj = nflds * nbias) %>% 
  select(aoi, tile, muarea, muarea_adj, fbias, nflds, nflds_adj, nbias, ntiles)

# hist(fsizes_n_05$muarea)
brks <- c(-1, 0.001, 1, 2, 4, 6, 10, 15, 25, 50)
labs <- c("0", "<1", "1-2", "2-4", "4-6", "6-10", "10-15", "15-25", "25-50")
labsv <- c(1:(length(labs)))
fsizes_n_05_adj <- fsizes_n_05_adj %>% 
  mutate(
    Area = as.numeric(cut(muarea, breaks = brks, labels = labsv)), 
    Area_adj = as.numeric(cut(muarea_adj, breaks = brks, labels = labsv))
  )

nbrks <- c(-1, 0.001, 50, 100, 200, 300, 400, 500, 700, 1000)
nlabs <- c("0", "<50", "50-100", "100-200", "200-300", "300-400", "400-500",
           "500-700", "700-1000")
nlabsv <- c(1:(length(labs)))
fsizes_n_05_adj <- fsizes_n_05_adj %>% 
  mutate(
    N = as.numeric(cut(nflds, breaks = nbrks, labels = nlabsv)), 
    N_adj = as.numeric(cut(nflds_adj, breaks = nbrks, labels = nlabsv))
  )

muarea <- st_rasterize(fsizes_n_05_adj["Area"])
muarea_adj <- st_rasterize(fsizes_n_05_adj["Area_adj"])
nflds <- st_rasterize(fsizes_n_05_adj["N"])
nflds_adj <- st_rasterize(fsizes_n_05_adj["N_adj"])

# plot(muarea)
# plot(nflds)
# plot(is.na(nflds))
# 
# fsizes_n_05 %>% filter(is.na(nflds))
# fsizes_n_05 %>% filter(is.infinite(nflds))
# plot(fsizes_n_05 %>% filter(is.na(nflds)))
thm <- function(x) {
  theme_void() + 
    theme(legend.position = c(0.7, 0.07), legend.direction = "horizontal", 
          legend.key.height = unit(0.2, "cm"), 
          legend.text = element_text(colour = "black"),
          legend.title = element_text(size = 9, colour = "black"))
}

leg <- c(labs, "")
xylims <- st_bbox(ghana)
p <- ggplot(africa) + 
  geom_sf(fill = "gray40", color = "grey", size = 0.25) +  
  geom_stars(data = muarea, aes(x = x, y = y, fill = factor(Area))) +
  geom_sf(data = aois, size = 0.1, fill = "transparent", col = "grey") +
  scale_fill_viridis_d(name = "ha", na.value = "transparent", labels = leg) +
  coord_sf(xlim = xylims[c(1, 3)], ylim = xylims[c(2, 4)]) + thm()
padj <- ggplot(africa) + 
  geom_sf(fill = "gray40", color = "grey", size = 0.25) +  
  geom_stars(data = muarea_adj, aes(x = x, y = y, fill = factor(Area_adj))) +
  geom_sf(data = aois, size = 0.1, fill = "transparent", col = "grey") +
  scale_fill_viridis_d(name = "ha", na.value = "transparent", labels = leg) +
  coord_sf(xlim = xylims[c(1, 3)], ylim = xylims[c(2, 4)]) + thm()

leg <- c(nlabs, "")
p2 <- ggplot(africa) + 
  geom_sf(fill = "gray40", color = "grey", size = 0.25) +  
  geom_stars(data = nflds, aes(x = x, y = y, fill = factor(N))) +
  # geom_stars(data = nflds) +
  geom_sf(data = aois, size = 0.1, fill = "transparent", col = "grey") +
  scale_fill_viridis_d(name = "ha", na.value = "transparent", labels = leg) +
  # scale_fill_viridis_c(name = "N", na.value = "transparent") +
  coord_sf(xlim = xylims[c(1, 3)], ylim = xylims[c(2, 4)]) + thm()
p2adj <- ggplot(africa) + 
  geom_sf(fill = "gray40", color = "grey", size = 0.25) +  
  geom_stars(data = nflds_adj, aes(x = x, y = y, fill = factor(N_adj))) +
  # geom_stars(data = nflds) +
  geom_sf(data = aois, size = 0.1, fill = "transparent", col = "grey") +
  scale_fill_viridis_d(name = "ha", na.value = "transparent", labels = leg) +
  # scale_fill_viridis_c(name = "N", na.value = "transparent") +
  coord_sf(xlim = xylims[c(1, 3)], ylim = xylims[c(2, 4)]) + thm()

p2adj

op <- p + p2 + plot_annotation(tag_levels = 'A')

ggsave(op, bg = "transparent", width = 6, height = 4, units = "in", dpi = 300, 
       filename = pth("figures/si_fsize_n_05.png"))
```

@@

m2 <- ggplot(aez %>% filter(ID != 8)) + geom_sf(lwd = 0.1) +
  geom_sf(data = aez_zones, lwd = 0.5, fill = "transparent") + 
  geom_sf_text(data = st_centroid(aez) %>% filter(ID != 8) %>% arrange(ID),
               aes(label = ID), 
               nudge_x = c(0.75, 0, 0, -1.25, -1, -1.25, 0),
               nudge_y = c(0.25, 0, 0, 0.7, 0.25, 1, 0),
               size = 3, col = "grey60") + 
  geom_sf_text(data = st_centroid(aez_zones), aes(label = zone), size = 4) + 
  theme_void() + theme(plot.margin = unit(c(0, 0, 0, 0), "cm"))
ggsave(m + m2 + plot_annotation(tag_levels = 'A'), 
       filename = pth("figures/si_aoi_zones.png"), width = 3.5 * 2, 
       height = 4.5, units = "in", dpi = 300)
```

### Table S4: AEZ accuracies

@@

### Figures S10 and S11: Segmentation statistics (grid scale)

```{r segstats, eval=FALSE}
# data("top_label_data")
# data("field_validation_stats")
data("segment_quality_stats")
# data
datnms <- c("top_label_data", "field_validation_stats")#,
            # "tile_aoi_validation_stats")
for(i in datnms) {
  load(system.file(glue::glue("extdata/{i}.rda"), package = "activemapper"))
}

@@

### Figure S12: Average fields sizes

Tile scale field size and number, presented without adjustment

```{r, eval=FALSE}
fsizes_n_05 <- st_read(
  system.file("extdata/field_size_n_05.geojson", package = "activemapper")
) %>% mutate(
  muarea = ifelse(is.na(muarea), 0, muarea),
  nflds = ifelse(is.na(nflds), 0, nflds),
  aoi = as.character(aoi)
)

# # calculate bias factors for adjustment
# data("segment_quality_stats")
# segment_quality_stats %>% filter(measure == "n")
# biases <- segment_quality_stats %>%
#   filter(Stat == "Mean" & scale == "grid") %>% 
#   pivot_wider(names_from = type, values_from = value) %>% 
#   mutate(bias = Validation - Segmentation, 
#          biasfactor = Validation / Segmentation)
# biases <- as_tibble(tiles) %>% group_by(aoi1) %>% 
#   count() %>% ungroup() %>% 
#   rename(aoi = aoi1, ntiles = n) %>% 
#   mutate(aoi = as.character(aoi), ncells = ntiles * 100) %>% 
#   left_join(biases, .) %>% 
#   select(-scale, -Stat)
# # biases %>% filter(measure == "n")
# # tiles %>% slice(1) %>% raster::extract(mgridr, .)
# # st_area(aois) / 10000 / 100
# 
# # apply bias adjustments
# # field area first
# fsizes_n_05_adj <- biases %>% filter(measure == "area" & aoi != "All") %>% 
#   select(aoi, biasfactor) %>% 
#   rename(fbias = biasfactor) %>% 
#   left_join(fsizes_n_05, .) %>% 
#   mutate(muarea_adj = muarea * fbias) 
# 
# # then field count
# fsizes_n_05_adj <- biases %>% filter(measure == "n" & aoi != "All") %>% 
#   select(aoi, biasfactor, ntiles, ncells) %>% 
#   rename(nbias = biasfactor) %>% 
#   left_join(fsizes_n_05_adj, .) %>% 
#   mutate(nflds_adj = nflds * nbias) %>% 
#   select(aoi, tile, muarea, muarea_adj, fbias, nflds, nflds_adj, nbias, ntiles)
# 
# 
# # hist(fsizes_n_05$muarea)
# brks <- c(-1, 0.001, 1, 2, 4, 6, 10, 15, 25, 50)
# labs <- c("0", "<1", "1-2", "2-4", "4-6", "6-10", "10-15", "15-25", "25-50")
# labsv <- c(1:(length(labs)))
# fsizes_n_05_adj <- fsizes_n_05_adj %>% 
#   mutate(
#     Area = as.numeric(cut(muarea, breaks = brks, labels = labsv)), 
#     Area_adj = as.numeric(cut(muarea_adj, breaks = brks, labels = labsv))
#   )
# 
# nbrks <- c(-1, 0.001, 50, 100, 200, 300, 400, 500, 700, 1000)
# nlabs <- c("0", "<50", "50-100", "100-200", "200-300", "300-400", "400-500",
#            "500-700", "700-1000")
# nlabsv <- c(1:(length(labs)))
# fsizes_n_05_adj <- fsizes_n_05_adj %>% 
#   mutate(
#     N = as.numeric(cut(nflds, breaks = nbrks, labels = nlabsv)), 
#     N_adj = as.numeric(cut(nflds_adj, breaks = nbrks, labels = nlabsv))
#   )
# 
# # stars
# muarea <- st_rasterize(fsizes_n_05_adj["Area"])
# muarea_adj <- st_rasterize(fsizes_n_05_adj["Area_adj"])
# nflds <- st_rasterize(fsizes_n_05_adj["N"])
# nflds_adj <- st_rasterize(fsizes_n_05_adj["N_adj"])

brks <- c(-1, 0.001, 1, 2, 4, 6, 10, 15, 25, 50)
labs <- c("0", "<1", "1-2", "2-4", "4-6", "6-10", "10-15", "15-25", "25-50")
labsv <- c(1:(length(labs)))
fsizes_n_05 <- fsizes_n_05 %>% 
  mutate(Area = as.numeric(cut(muarea, breaks = brks, labels = labsv)))

# hist(fsizes_n_05$nflds)
nbrks <- c(-1, 0.001, 50, 100, 200, 300, 400, 500)
nlabs <- c("0", "<50", "50-100", "100-200", "200-300", "300-400", "400-500")
nlabsv <- c(1:(length(nlabs)))
fsizes_n_05 <- fsizes_n_05 %>% 
  mutate(N = as.numeric(cut(nflds, breaks = nbrks, labels = nlabsv)))

muarea <- st_rasterize(fsizes_n_05["Area"])
nflds <- st_rasterize(fsizes_n_05["N"])

thm <- function(x) {
  theme_void() + 
    theme(#legend.position = c(0.7, 0.07), 
          legend.direction = "vertical", 
          legend.key.height = unit(0.2, "cm"), 
          legend.text = element_text(colour = "black"),
          legend.title = element_text(size = 9, colour = "black"))
}

leg <- c(labs, "")
xylims <- st_bbox(ghana)
p <- ggplot(africa) + 
  geom_sf(fill = "gray40", color = "grey", size = 0.25) +  
  geom_stars(data = muarea, aes(x = x, y = y, fill = factor(Area))) +
  geom_sf(data = aois, size = 0.1, fill = "transparent", col = "grey") +
  scale_fill_viridis_d(name = "ha", na.value = "transparent", labels = leg) +
  coord_sf(xlim = xylims[c(1, 3)], ylim = xylims[c(2, 4)]) + thm()
# padj <- ggplot(africa) + 
#   geom_sf(fill = "gray40", color = "grey", size = 0.25) +  
#   geom_stars(data = muarea_adj, aes(x = x, y = y, fill = factor(Area_adj))) +
#   geom_sf(data = aois, size = 0.1, fill = "transparent", col = "grey") +
#   scale_fill_viridis_d(name = "ha", na.value = "transparent", labels = leg) +
#   coord_sf(xlim = xylims[c(1, 3)], ylim = xylims[c(2, 4)]) + thm()

leg <- c(nlabs, "")
p2 <- ggplot(africa) + 
  geom_sf(fill = "gray40", color = "grey", size = 0.25) +  
  geom_stars(data = nflds, aes(x = x, y = y, fill = factor(N))) +
  geom_sf(data = aois, size = 0.1, fill = "transparent", col = "grey") +
  scale_fill_viridis_d(name = "N", na.value = "transparent", labels = leg) +
  coord_sf(xlim = xylims[c(1, 3)], ylim = xylims[c(2, 4)]) + thm()
# p2adj <- ggplot(africa) + 
#   geom_sf(fill = "gray40", color = "grey", size = 0.25) +  
#   geom_stars(data = nflds_adj, aes(x = x, y = y, fill = factor(N_adj))) +
#   geom_sf(data = aois, size = 0.1, fill = "transparent", col = "grey") +
#   scale_fill_viridis_d(name = "ha", na.value = "transparent", labels = leg) +
#   coord_sf(xlim = xylims[c(1, 3)], ylim = xylims[c(2, 4)]) + thm()

op <- p + p2 + plot_annotation(tag_levels = 'A')

ggsave(op, bg = "transparent", width = 7, height = 4, units = "in", dpi = 300, 
       filename = pth("figures/si_fsize_n_05.png"))
```

Both original as derived from segmentations and adjusted using regression kriging.

```{r, eval=FALSE}
fsizes <- read_stars(
  system.file("extdata/mean_field_size005.tif", package = "activemapper")
)
fsizes_adj <- read_stars(
  system.file("extdata/mean_field_size005_adj.tif", package = "activemapper")
)

# Plots
xylims <- st_bbox(ghana)
p <- ggplot(africa) + 
  geom_sf(fill = "gray40", color = "grey", size = 0.25) +  
  geom_stars(data = fsizes) +
  geom_sf(data = aois, size = 0.1, fill = "transparent", col = "grey") +
  scale_fill_viridis_c(name = "ha", na.value = "transparent") +
  coord_sf(xlim = xylims[c(1, 3)], ylim = xylims[c(2, 4)]) +
  theme_void() + 
  theme(legend.position = c(0.7, 0.07), legend.direction = "horizontal", 
        legend.key.height = unit(0.2, "cm"), 
        legend.text = element_text(colour = "black"),
        legend.title = element_text(size = 9, colour = "black"))

p2 <- ggplot(africa) + 
  geom_sf(fill = "gray40", color = "grey", size = 0.25) +  
  geom_stars(data = fsizes_adj[, , , 1]) +
  geom_sf(data = aois, size = 0.1, fill = "transparent", col = "grey") +
  scale_fill_viridis_c(name = "ha", na.value = "transparent") +
  coord_sf(xlim = xylims[c(1, 3)], ylim = xylims[c(2, 4)]) +
  theme_void() + 
  theme(legend.position = c(0.7, 0.07), legend.direction = "horizontal", 
        legend.key.height = unit(0.2, "cm"), 
        legend.text = element_text(colour = "black"),
        legend.title = element_text(size = 9, colour = "black"))

op <- p + p2 + plot_annotation(tag_levels = 'A')

ggsave(op, bg = "transparent", width = 6, height = 4, units = "in", dpi = 300, 
       filename = pth("figures/si_fsizes.png"))

### 2021-02-22 inst/manuscript/manuscript.Rmd
Additional accuracy metrics added to SI.
Edits for average field size text (SI, ms), and regression kriging adjustments (not to be retained), as well as new tile-wise presentation (figures).

---
title: "Improving cropland maps through tight integration of human and machine intelligence"

@@

- name: Qi Zhang
  affilnum: '1'

@@

## Map accuracy
### Categorical accuracy
To assess the overall accuracy of the final maps, we used our map reference sample to evaluate the accuracy of classifications derived from thresholding the posterior probabilities produced by the RandomForest model, as well as the segmented field boundary maps. First, we evaluated the inter-rater agreement between reference supervisors in labeling reference polygons. The average inter-rater agreement was **X%, with a standard deviation of Y% (see Figure X in SI)**, which provides the upper bound on achievable map accuracy.

Based on this reference sample, we found that the average accuracy of the pixel-wise classifications was **X, with a range of X-X** (Figure 5). Overall user's accuracy was slightly **lower/higher** at **X, (range X-X)**, while producer's accuracy averaged **X, (range X-X)**. Each accuracy measure was highest in **northern-northeastern 2/3** of the country, and lowest in **southwestern 1/3**, where rainfall and cloud-cover are highest, and where tree crops dominate. The segmentation process **increased/decreased** accuracy slightly, with a mean overall, user's and producer's accuracy of **X (range X-X), Y (range X-X), and Z (range X-X) percent**.

@@

The accuracy patterns generally align with the difficulty of the labelling task, that is, **the southwestern regions were hardest for workers to interpret, as shown by Figure 5.**

@@

## Ghana's croplands
Two separate maps of cropland were produced for each AOI, one derived from the cropland probability map, and the other from the segmented field boundaries.

Map figure:
- Panel A: Cropland probability map (0.005 degree resolution)
  - Panel A insets: Probability close-ups in AOIs 1, 8, 13, 15
- Panel B: Cropland percentage map (0.005 degree)
  - Panel B insets: Segment close-ups in AOIs 1, 8, 13, 15
- Panel C: Median field size
- Panel D: Field number
- Median field size
- Cropland percentage

Stats figure: 
- Mean field size per AOI
- Median field size per AOI
- SD fields per AOI 
- N field per AOI

```{r mainmap, echo = FALSE, out.width="90%", fig.cap="The distribution of arable croplands in Ghana. The main map shows the percentage of croplands in each 0.005 degree grid cell, derived from the predicted cropland probabilities. The insets  on the margins illustrate predicted probabilities (top map in each couplet) at original resolution (0.000025 degrees) and segmented field boundaries overlaid on the dry season PlanetScope composite, for four separate tiles. Each tile's position is shown on the main map, and is color-coded to the boundary lines around its corresponding inset.", fig.align='center', message=FALSE}
knitr::include_graphics('figures/figure8.png')
```

# Discussion
- Label quality
  - Accuracy asssessment at training reference sites maybe over-inflated. Each worker saw training reference site multiple times. Need larger number of reference samples
  - Training reference to training ratio was artificially inflated. Workers not always notified when training labels complete, and thus only served training reference sites. 
  - Image-interpreted versus ground labels: **However, these discrepancies are not necessarily an indication of how far workers were from the "truth", but may instead be at least partially an indication of how different the perspectives are as to what constitutes a field when looking at an image versus seeing it from the ground (which in many cases was based on the field team's judgement, rather than farmer guidance).**

>>>>

---
title: "Mapping the characteristics of small-scale agricultural systems at national extents using small sat data and an active learning approach"

@@

@@

## Map accuracy
### Categorical accuracy
```{r, echo=FALSE, message=FALSE, warning=FALSE}
# reference labels, for total count and uncertainty of class categories
ref_labels <- st_read(
  system.file("extdata/map_reference_labels.geojson", 
              package = "activemapper"), quiet = TRUE
)
class_ct <- as_tibble(ref_labels) %>% group_by(category) %>% count()
ref_ct <- as_tibble(ref_labels) %>% group_by(worker_id) %>% count() %>% pull(n)

crp_ct <- class_ct %>% filter(category %in% c("annualcropland", "unsure1"))
noncrp_ct <- class_ct %>% filter(category %in% c("noncropland", "unsure2"))

# observer agreement/correlation
ref_labels_joint <- st_read(
  system.file("extdata/map_reference_labels_joint.geojson", 
              package = "activemapper"), quiet = TRUE
)
joint_classes <- ref_labels_joint %>% as_tibble() %>% 
  select(name, category, worker_id) %>% 
  arrange(name) %>% 
  mutate(class = case_when(
    category == "annualcropland" | category == "unsure1" ~ 1, 
    category == "noncropland" | category == "unsure2" ~ 0 
  ))
class_mat <- joint_classes %>% dplyr::select(name, class, worker_id) %>% 
  tidyr::pivot_wider(names_from = worker_id, values_from = class) %>% 
  dplyr::select(-name) %>% as.matrix()

usertab <- table("User1" = class_mat[, 1], "User2" = class_mat[, 2])

agreement <- round(sum(diag(usertab)) / sum(usertab) * 100, 1)
observer_r <- cor.test(class_mat[, 1], class_mat[, 2], method = "spearman")

To assess the overall accuracy of the final maps, we used our map reference sample of `r sum(ref_ct)` sites (`r sum(crp_ct$n)` cropland; `r sum(noncrp_ct$n)` non-cropland) to evaluate the accuracy of 1) pixel-wise classifications produced by the RandomForest model, and 2) the segmented field boundary maps. We first evaluated the uncertainty in the map reference classes using two approaches, the first being an assessment of the overall agreement between map reference labels (at `r sum(usertab)` sites), and the second was the level of confidence in assigned labels (see SI for details). The first measure showed that the two individual labellers agreed `r agreement`% of sites, while the second showed that `r round(sum(crp_ct$n[2], noncrp_ct$n[2]) / sum(ref_ct) * 100, 1)` of sites labelled were of lower confidence.

Based on this reference sample, we found that the overall accuracy of the pixel-wise classifications was 88% (Table 2). This overall level of accuracy varied within four smaller zones (Figure S9A), ranging from 83.3% in Zone 1 (comprised of AOIs 1-3) to 93.6% in Zone 3 (AOIs 10, 11, 13, 15, and 16). Examining the accuracies of the individual classes, the Producer's accuracy of the cropland class was 61.7% across Ghana, ranging from 45.6% in Zone 3 to 67.9% in Zone 1. The User's accuracy for cropland was 67.3% overall, ranging from 59.8% in Zone 4 to 71.2% in Zone 1. Both measures of accuracy were substantially higher for the non-cropland class across all zones, typically exceeding 90%, with the lowest accuracies for this class found in Zone 1 (Producer's = 89.3% and User's = 87.7%, respectively).

The overall accuracies obtained from the segmented maps were generally 1-2 percentage points lower than those of the per-pixel maps, while User's accuracies tended to be 8-10 percentage points less (Table 2). In contrast, Producer's accuracies were 15-20 points higher than in the per-pixel map, indicating that the segmentation step helped reduce omission error, but substantially increased false positive errors.

@@

\begin{table}
\caption{Map accuracies and adjusted area estimates for the ~3 m pixel-wise classifications (based on RandomForest predictions; top 5 rows) and the segmented map (bottom 5 rows). Results are provided for 4 zones (Zone 1 = AOIs 1-3; Zone 2 = AOIs 4-9; Zone 3 = AOIs 10, 11, 13, 14, 16; Zone 4 = AOIs 12, 15) plus the entire country. The error matrix (with reference values in columns) provides the areal percentage for each cell, and the producer's (P), user's (U), and overall (O) map accuracies and their margins of error (in parenthesis) are provided, as well as the sample-adjusted area estimates (in km$^{2}$) and margins of error. }
\includegraphics[width = 18cm]{figures/table2.png}
\label{tab:aezaccuracy}
\end{table}

@@

## Ghana's croplands
Two separate maps of cropland were produced for each AOI, the per-pixel classified from the cropland probabilities, and the vectorized map of field boundaries (Figure \ref{fig:mainmap}). The former map provides the more accurate assessment of the distribution of croplands in Ghana, which are most concentrated in the Southeastern corner (AOI 15), the central-western region (AOI 7, the northeastern and northwestern corners of AOIs 10 and 11, and the south of AOI 8), the northeastern quadrant stretching from AOI 9 through 5 and 6 up to 2 and 3. The northern third of AOI 1 also has noticeable densities of cropland. Several noteable areas of low cropland density are also apparent, indicating the presence of large protected areas, such as Mole National Park in the the southeastern corner of AOI 1 and Digya National Park in the northwestern corner of AOI 12. In contrast, the relative absence of cropland in AOIs 13, 14, and 16 do not reflect the scarcity of agriculture, but rather the predominance of tree-based agriculture in the forested agroecoregions of Ghana, which was not mapped.

```{r mainmap, echo = FALSE, out.width="90%", fig.cap="The distribution of arable croplands in Ghana. The main map shows the percentage of croplands in each 0.005 degree grid cell, derived from the predicted cropland probabilities. The insets  on the margins illustrate predicted probabilities (top map in each couplet) at original resolution (0.000025 degrees) and segmented field boundaries overlaid on the dry season PlanetScope composite, for four separate tiles. Each tile's position is shown on the main map, and is color-coded to the boundary lines around its corresponding inset.", fig.align='center', message=FALSE}
knitr::include_graphics('figures/figure7.png')
```

Both the per-pixel and vectorized maps, when combined with the map reference sample, enable separate estimates of the total extent of arable croplands in Ghana. The cropland extent estimated from the vectorized map is 42,359 km$^2$ (with a margin of error of 4,395 km$^2$), or `r round(42359 / (42359 + 204940) * 100, 1)`% of the mapped area, the estimate based on the per pixel map is 43,233 km$^2$ (margin of error = 4,904 km$^2$), or `r round(43233 / (43233 + 202856) * 100, 1)`% of area.

The vectorized map provides additional information on how the characteristics of croplands can vary geographically, ranging from narrow, strip-like fields in parts of AOI 15 (Figure 7's lower right inset) to more densely packed, less distinctly shaped fields in area such as AOI 5 (upper right inset in Figure 7). These characteristics can be summarized and mapped to explore how such characteristics vary geographically For example, average fields sizes were mapped at 0.005 degree resolution (Figure S12A), providing some indication of countrywide patterns. Given the over-estimation of fields sizes relative to the validation labels, particularly in several savanna-zone AOIs (2, 3, 6, 7, and 15), the mean sizes likely reflect agglomerations of contiguous smallholder fields, such as in AOI 2,and the southern portion of AOI 8 (Figure S12A). A closer approximation of individual field boundaries can be mapped using approaches such as regression kriging to model the relationship between the segmented boundaries and the hand drawn labels collected at validation points (Figure S12B), although such an approach introduces spatial artifacts.

# Discussion
We present here a method for developing high resolution maps that detail the characteristics of smallholder-dominated croplands, providing information on their geometries and distribution of <5 m resolution, and representing a single agricultural year.

The results

- Label quality
  - Accuracy asssessment at training reference sites maybe over-inflated. Each worker saw training reference site multiple times. Need larger number of reference samples
  - Training reference to training ratio was artificially inflated. Workers not always notified when training labels complete, and thus only served training reference sites. 
  - Image-interpreted versus ground labels: **However, these discrepancies are not necessarily an indication of how far workers were from the "truth", but may instead be at least partially an indication of how different the perspectives are as to what constitutes a field when looking at an image versus seeing it from the ground (which in many cases was based on the field team's judgement, rather than farmer guidance).**

Compare values

### 2021-02-22 inst/manuscript/si.Rmd
Edits for average field size text (SI, ms), and regression kriging adjustments (not to be retained), as well as new tile-wise presentation (figures).

@@

The total validation sample was `r sum(ref_ct)`, with `r ref_ct[2]` samples collected and interpreted by one observer (Su Ye) and `r ref_ct[1]` collected by a second observer (Estes). To evaluate the uncertainty inherent in defining the map reference labels, the pair both mapped `r sum(usertab)` sites, showing an overall level of agreement of `r agreement`%, and a Spearman Rank Correlation of `r round(unname(observer_r$estimate), 2)`.

@@

### Categorical accuracy
In addition to the map accuracies and area estimates calculated per AOI zone (reported in main text; see Figure \ref{tab:aoizones}A), the accuracies were also assessed within several different groupings of agroecozones (Figures \ref{fig:aoizones}B) and \ref{fig:aezaccuracy}).

```{r aoizones, echo = FALSE, out.width="100%", fig.cap="Four zones used to combine the A) AOIs and B) agroecozones (B), in order to assess sub-national mapping accuracy. ", fig.align='center', message=FALSE, results='hold'}
knitr::include_graphics('figures/si_aoi_zones.png')
```

```{r aezaccuracy, echo = FALSE, out.width="100%", fig.cap="Map accuracies and adjusted area estimates within four different groupings of Ghana's agroecozones", fig.align='center', message=FALSE, results='hold'}
knitr::include_graphics('figures/si_aez_accuracies.png')
```

@@

>>>>

knitr::opts_chunk$set(fig.pos = "!ht", out.extra = "")

@@

The total validation sample was `r sum(ref_ct)`, with `r ref_ct[2]` samples collected and interpreted by one observer (Su Ye) and `r ref_ct[1]` collected by a second observer (Estes). To evaluate the uncertainty inherent in defining the map reference labels, the pair mapped `r sum(usertab)` common sites, showing an overall level of agreement of `r agreement`%, and a Spearman Rank Correlation of `r round(unname(observer_r$estimate), 2)`.

@@

### Categorical accuracy
In addition to the map accuracies and area estimates calculated per AOI zone (reported in main text; see Figure \ref{fig:aoizones}A), the accuracies were also assessed within several different groupings of agroecozones (Figures \ref{fig:aoizones}B and Table \ref{tab:aezaccuracy}).

```{r aoizones, echo = FALSE, out.width="100%", fig.cap="Four zones used to combine the A) AOIs and B) agroecozones (B), in order to assess sub-national mapping accuracy. In B, the ID number of Ghana's individual agroecozones is shown in grey: 1 = Coastal savanna; 2 = Wet evergreen; 3 = Moist evergreen; 4 = Deciduous forest; 5 = Transitional zone; 6 = Guinea savanna; 7 = Sudan savanna; 8 (not shown) = Volta Lake.", fig.align='center', message=FALSE, results='hold'}
knitr::include_graphics('figures/si_aoi_zones.png')
```

\begin{table}
\caption{Map accuracies and adjusted area estimates for the ~3 m pixel-wise classifications (based on RandomForest predictions). Results are provided for four different groupings of Ghana's 8 agroecozones zones (Zone 1 = Coastal savanna; Zone 2 = Wet evergreen, Moist evergreen, and Deciduous forest; Zone 3 = Transitional zone; Zone 4 = Guinea savanna and Sudan savanna) plus the entire country. The error matrix (with reference values in columns) provides the areal percentage for each cell, and the producer's (P), user's (U), and overall (O) map accuracies and their margins of error (in parenthesis) are provided, as well as the sample-adjusted area estimates (in km$^{2}$) and margins of error.}
\includegraphics[width = 18cm]{figures/si_aez_accuracies.png}
\label{tab:aezaccuracy}
\end{table}

@@

## Cropland characteristics
### Average field size

To examine average field sizes, the average area of the vectorized field boundaries intersecting each 0.005 degree cell in the mapping grid was calculated and mapped back onto the grid (Figure \ref{fig:fieldsize}A). Given the overestimation bias inherent in the vectorized boundaries relative to the hand-digitized validation labels, we also used a regression kriging approach [@henglRegressionkrigingEquationsCase2007] to these average field sizes for this bias. To do this, we used the estimated mean field sizes extracted from the map in Figure S12A to predict the average polygon size of the most accurate mapper's labels for each of the 1600 validation sites, using an ordinary least squares regression to model the relationship, after first log-transforming both variables. We then applied ordinary kriging (using an exponential model for the variogram) to the regression residuals, which we added to the surface of the predicted field sizes to create the adjusted surface, and then converted this back to units of hectares (Figure \ref{fig:fieldsize}B).

```{r fieldsizes, echo = FALSE, out.width="100%", fig.cap="Average fields sizes in Ghana at 0.005 degree resolution, as calculated from A) the vectorized field boundaries, and after B) adjustment against hand-drawn validation labels using a regression-kriging approach.", fig.align='center', message=FALSE, results='hold'}
knitr::include_graphics('figures/si_fsizes.png')
```
